\documentclass{book}

\usepackage{makeidx}
\makeindex

\begin{document}

\frontmatter

\begin{titlepage}
    \centering
    \vspace*{\fill}
    {\Huge\bfseries Probability theory and statistical inference\par}
    \vspace{1cm}
    {\Large Jesus Urtasun Elizari\par}
    \vspace{1cm}
    {\large\today\par}
    \vspace*{\fill}
\end{titlepage}

\tableofcontents

\chapter*{Index}
\addcontentsline{toc}{chapter}{Index}
\printindex

\mainmatter

\chapter*{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

\section{Background}
\indent In the following pages one will find an introductory text to one of the key subjects within mathematical sciences. The text is composed by four chapters, together with some appendix reviewing basic mathematical concepts, and a bibliographic note. The purpose of this lecture notes is to make both probability and statistical analysis an easy, interesting and engaging topic for anyone interested, without the need for prior experience with mathematical training.\\

First, we will introduce and explore the concept of probability itself, and we will discuss how to model information, surprise, and various random processes, also referred to as stochastic. Then we will introduce the idea of a function and how functions need to be adapted to implement uncertainty when discussing random events

\chapter{Introduction to probability theory}

\section{What is probability?}
Your content for Chapter 1 goes here.

\section{Discrete probability distributions}
Your content for Chapter 1 goes here.

\section{Continuous probability distributions}
Your content for Chapter 1 goes here.

\chapter{Liinear models}

\section{Functions and variables}
Your content for Chapter 2 goes here.

\section{Modelling uncertainty in random events}
Your content for Chapter 2 goes here.

\chapter{Introduction to statistical inference}

\section{Hypothesis testing}
Your content for Chapter 3 goes here.

\section{The idea of significance and p-values}
Your content for Chapter 3 goes here.

\section{Parametric and non parametric tests}
Your content for Chapter 3 goes here.

\chapter{Introduction to bayesian statistics}

\section{Frequentist and bayesian approach}
Your content for Chapter 4 goes here.

\section{Bayesian statistics}
Your content for Chapter 4 goes here.

\backmatter

\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plain} % Choose your bibliography style
\bibliography{your_bibliography_file} % Replace with your actual .bib file

\end{document}